Checkpoint 4

### 2020-04-30 Checkpoint 4.Rmd
cleaning house

```{r}
################################## To do before Alicia with your fave model ##########################################
# mcmc_trace()
# mcmc_dens_overlay()
# pp_check()

### For predicting one case 
          # new_308 <- data.frame(Days = 9, Subject =308)
          # 
          # set.seed(454)
          # pred_308 <- posterior_predict(
          #   model_4, 
          #   newdata = new_308)
          # 
          # pred_308 <- data.frame(y_new = pred_308[-1])
          # 
          # ggplot(pred_308, aes(x=y_new))+geom_density()
          # 
          # summary(pred_308)

## For correlation check (type like model 2 from activity 19)
          # Store the chains
          # model_1_df <- as.array(model_1) %>% 
          #   melt %>% 
          #   pivot_wider(names_from = parameters, values_from = value)
          # 
          # # Wrangle the chains
          # # Note the need for `...` around the sigma_sq_b
          # model_1_df <- model_1_df %>% 
          #   mutate(sigma_sq_w = `sigma`, sigma_sq_b = `Sigma[Region:(Intercept),(Intercept)]`) %>% 
          #   mutate(correlation = (sigma_sq_b/(sigma_sq_w+sigma_sq_b)))
          # 
          # ggplot(model_1_df, aes(x = correlation)) + 
          #   geom_density(alpha = 0.5)
```

@@

#Quinn making models
```{r, cahce=TRUE}
# 
# model_1 <- stan_glmer(
#   ChinaVirusInterest ~ (1 | State), #Gives us random intercepts
#   data = Finaldata, family = gaussian, chains = 4, iter = 5000*2
# )
```

```{r}
# head(data.frame(summary(model_1)),-2)
```

#Quinn making models
```{r, warning=FALSE, cache=TRUE}
# model_2 <- stan_glmer(
#   ChinaVirusInterest ~ Day + (Day | State),
#   data = Finaldata, family = gaussian,
#   chains = 4, iter = 100, refresh = 0
# )

```{r}
# head(data.frame(summary(model_2)),-2)
```

#Quinn makes models
```{r, warning = FALSE, cache=TRUE}
# model_3 <- stan_glmer(
#   ChinaVirusInterest ~ Day + StateColor + (Day | State),#Random intercepts and slopes when we put Day in
#   data = Finaldata, family = gaussian,
#   chains = 4, iter = 100, refresh = 0
# )
```

```{r}
# head(data.frame(summary(model_3)),-2)
```

#Quinn makes models
```{r, warning = FALSE, cache=TRUE}
# model_4 <- stan_glmer(
#   ChinaVirusInterest ~ Day + totalTestResults + (Day | State),#Random intercepts and slopes when we put Day in
#   data = Finaldata, family = gaussian,
#   chains = 4, iter = 100, refresh = 0
# )
```

```{r}
# head(data.frame(summary(model_4)),-2)
```

@@

```{r}
head(data.frame(summary(model_100)),-2)
```
```{r}
mcmc_trace(model_100)
mcmc_dens_overlay(model_100) 
```

@@

# pred_5 <- posterior_predict(
#   model_5,
#   newdata = Finaldata, transform = TRUE)

prediction_summary(y = Finaldata$ChinaVirusInterest,
  yrep = pred_1)

# prediction_summary(y = Finaldata$ChinaVirusInterest,
#   yrep = pred_5)
```

```{r}
### For predicting one case 
new_CA <- Finaldata%>% 
          filter(State=="CA") #filter the row of interest

set.seed(454)
pred_CA <- posterior_predict(
  model_100,
  newdata = new_CA)

pred_2 <- data.frame(y_new = pred_CA[-1])

@@

```{r}
# For correlation check (type like model 2 from activity 19)
# Store the chains
model_2_df <- as.array(model_2) %>%
  melt %>%
  pivot_wider(names_from = parameters, values_from = value)

# Wrangle the chains
# Note the need for `...` around the sigma_sq_b
model_2_df <- model_2_df %>%
  mutate(sigma_sq_w = `sigma`, sigma_sq_b = `Sigma[State:(Intercept),(Intercept)]`) %>%
  mutate(correlation = (sigma_sq_b/(sigma_sq_w+sigma_sq_b)))

ggplot(model_2_df, aes(x = correlation)) +
  geom_density(alpha = 0.5)
```

@@

```{r}
#set.seed(454)
my_data <- data.frame(StateColor = "blue", State = "FL", Day = 18336)
# Simulate a set of predictions for each case in newdata
#my_prediction <- posterior_predict(
 # model_5, 
  #newdata = my_data)

#my_prediction <- data.frame(y_new = my_prediction[,1])

#ggplot(my_prediction, aes(x = y_new)) + 
 # geom_density()

#summary(my_prediction)
```

##Model 9:

StateColor +percent_asian + totalTestResults + (StateColor | State)

model_9 <- stan_glmer(
  ChinaVirusInterest ~ StateColor +percent_asian + totalTestResults + (StateColor | State), #Gives us random intercepts
  data = Finaldata, family = gaussian, chains = 4, iter = 1000*2
)
```

```{r}
head(data.frame(summary(model_9)),-2)
```

```{r}
# y = original sample, yrep = MCMC simulation
set.seed(454)
pp_check(model_9, nreps = 50)
```

```{r}
# Store the chains
model_9_df <- as.array(model_9) %>% 
  melt %>% 
  pivot_wider(names_from = parameters, values_from = value)

# Wrangle the chains
# Note the need for `...` around the sigma_sq_b
model_9_df <- model_9_df %>% 
  mutate(sigma_sq_w = `sigma`, sigma_sq_b = `Sigma[State:(Intercept),(Intercept)]`) %>% 
  mutate(correlation = (sigma_sq_b/(sigma_sq_b+sigma_sq_w)))

ggplot(model_9_df, aes(x = correlation)) + 
  geom_density(alpha = 0.5)

```{r}
#set.seed(454)
my_data <- data.frame(StateColor = "red", State = "FL")

# Simulate a set of predictions for each case in newdata
my_prediction <- posterior_predict(
  model_9,
   newdata = my_data)

@@

colSums(is.na(model_data))
```
```{r}
model_10 <- stan_glmer(
  ChinaVirusInterest ~ Day + (1 | State) + percent_white,
  data = model_data, family = gaussian, chains = 4, iter = 1000
)
```
```{r}
head(data.frame(summary(model_10)),-2)
```

```{r}
# Store the chains
model_10_df <- as.array(model_10) %>% 
  melt %>% 
  pivot_wider(names_from = parameters, values_from = value)

# Wrangle the chains
# Note the need for `...` around the sigma_sq_b
model_10_df <- model_10_df %>% 
  mutate(sigma_sq_w = `sigma`, sigma_sq_b = `Sigma[State:(Intercept),(Intercept)]`) %>% 
  mutate(correlation = (sigma_sq_b/(sigma_sq_w+sigma_sq_b)))

ggplot(model_10_df, aes(x = correlation)) + 
  geom_density(alpha = 0.5)
```
```{r}
set.seed(454)
#random intercept and random slope, percent white
model_11 <- stan_glmer(
  ChinaVirusInterest ~ (Day | State) + percent_white,
  data = model_data, family = gaussian, chains = 4, iter = 3000
)
```
```{r}
head(data.frame(summary(model_11)),-2)
```

```{r}
# Store the chains
model_11_df <- as.array(model_11) %>% 
  melt %>% 
  pivot_wider(names_from = parameters, values_from = value)

# Wrangle the chains
# Note the need for `...` around the sigma_sq_b
model_11_df <- model_11_df %>% 
  mutate(sigma_sq_w = `sigma`, sigma_sq_b = `Sigma[State:(Intercept),(Intercept)]`) %>% 
  mutate(correlation = (sigma_sq_b/(sigma_sq_w+sigma_sq_b)))

ggplot(model_10_df, aes(x = correlation)) + 
  geom_density(alpha = 0.5)
```

```{r}
set.seed(454)

model_12<- stan_glmer(
  ChinaVirusInterest ~ Day + (1 | State) + percent_white +positive_rate,
  data = model_data, family = gaussian, chains = 4, iter = 3000
)
```
```{r}
head(data.frame(summary(model_12)),-2)
```

```{r}
# Store the chains
model_12_df <- as.array(model_12) %>% 
  melt %>% 
  pivot_wider(names_from = parameters, values_from = value)

# Wrangle the chains
# Note the need for `...` around the sigma_sq_b
model_12_df <- model_12_df %>% 
  mutate(sigma_sq_w = `sigma`, sigma_sq_b = `Sigma[State:(Intercept),(Intercept)]`) %>% 
  mutate(correlation = (sigma_sq_b/(sigma_sq_w+sigma_sq_b)))

ggplot(model_12_df, aes(x = correlation)) + 
  geom_density(alpha = 0.5)
```

@@

Model 14
```{r}
set.seed(454)
#Neg Rate
model_14 <- stan_glmer(
  ChinaVirusInterest ~ (1 | State) + negative_rate,
  data = mod_data, family = gaussian, chains = 4, iter = 1000
)
```

```{r}
head(data.frame(summary(model_14)),-2)
```

Checking Model 14
```{r}
mcmc_trace(model_14)
mcmc_dens(model_14)
```
```{r}
pp_check(model_14, nreps=50)
```

```{r}
# Store the chains
model_14_df <- as.array(model_14) %>% 
  melt %>% 
  pivot_wider(names_from = parameters, values_from = value)

# Wrangle the chains
# Note the need for `...` around the sigma_sq_b
model_14_df <- model_14_df %>% 
  mutate(sigma_sq_w = `sigma`, sigma_sq_b = `Sigma[State:(Intercept),(Intercept)]`) %>% 
  mutate(correlation = (sigma_sq_b/(sigma_sq_w+sigma_sq_b)))

ggplot(model_14_df, aes(x = correlation)) + 
  geom_density(alpha = 0.5)
```

 # Simulate a set of predictions for each case in newdata
my_prediction <- posterior_predict(
   model_14,
   newdata = my_data)

```{r}
model_15<-stan_glmer(
  ChinaVirusInterest ~ (Day|State) + negative_rate,
  data=mod_data, family=gaussian, chains =4, iter = 5000
)
```

@@

```{r}
# Store the chains
model_15_df <- as.array(model_15) %>%
  melt %>%
  pivot_wider(names_from = parameters, values_from = value)

# Wrangle the chains
# Note the need for `...` around the sigma_sq_b
model_15_df <- model_15_df %>%
  mutate(sigma_sq_w = `sigma`, sigma_sq_b = `Sigma[State:(Intercept),(Intercept)]`) %>%
  mutate(correlation = (sigma_sq_b/(sigma_sq_w+sigma_sq_b)))

ggplot(model_15_df, aes(x = correlation)) +
  geom_density(alpha = 0.5)
```

>>>>

@@

#Quinn making models

@@

```{r}
head(data.frame(summary(model_100)),-2)
```

```{r}
mcmc_trace(model_100)
mcmc_dens_overlay(model_100) 
```

@@

prediction_summary(y = Finaldata$ChinaVirusInterest,
  yrep = pred_1)
```

```{r}
### For predicting one case 
new_IL <- Finaldata%>% 
          filter(State=="IL") #filter the row of interest

set.seed(454)
pred_IL <- posterior_predict(
  model_100,
  newdata = new_IL)

pred_2 <- data.frame(y_new = pred_IL[-1])

@@

@@

```{r}
#set.seed(454)

my_prediction <- posterior_predict(
  model_5,
  newdata = new_IL)

@@

colSums(is.na(model_data))
```

@@

@@
